### 2017-05-10 papers/paper.tex
Adds paper outline

\documentclass{article}

\usepackage{indentfirst}
\usepackage{setspace}
\doublespacing

% ================================================================================= 
% Package for showing source code
% =================================================================================

\usepackage{listings}
\usepackage{color}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{frame=tb,
language=C,
aboveskip=.5mm,
belowskip=.5mm,
showstringspaces=false,
columns=flexible,
basicstyle={\scriptsize\ttfamily},
numbers=none,
numberstyle=\tiny\color{gray},
keywordstyle=\color{blue},
commentstyle=\color{dkgreen},
stringstyle=\color{mauve},
breaklines=false,
breakatwhitespace=true,
tabsize=3
}

% ================================================================================= 
% Package for flowcharts/diagrams
% =================================================================================

\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows}

\tikzstyle{startstop} = [rectangle, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=red!30]
\tikzstyle{io}        = [rectangle, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=blue!30]
\tikzstyle{process}   = [diamond, minimum width=2cm, minimum height=0cm, text centered, draw=black, fill=orange!30]
\tikzstyle{arrow}     = [thick,->,>=stealth]

% ==================================================
% Paper
% ==================================================

\title{DWave Interface for NP-complete problems}
\date{05-10-2017}
\author{Lucas Saldyt}

\begin{document}

\maketitle
\pagenumbering{gobble}
\newpage
\pagenumbering{arabic}

% ==================================================
\section{Abstract}
% ==================================================

Programming a quantum annealer to solve certain kinds of NP-complete problems is actually much simpler than one would expect.
Because of the rich software toolchains surrounding the DWave, it is easy to describe problems for the annealer to solve.
This paper compares various implementations of the Knapsack problem (and lightly covers other NP-complete problems).

% ==================================================
\section{Introduction}
% ==================================================

...

% ==================================================
\section{Methods}
% ==================================================

\begin{verbatim}
Classical solving:
    Python:
        Naive
        Dynamic Programming
        Polynomial Approximation

Quantum/Simulated solving:
    Verilog
    Prolog
    Grover's (qasm)

csv problem instance input(s)
\end{verbatim}

% ==================================================
\section{Discussion}
% ==================================================

Which interface is simplest? Easiest to use?
Simple interface must be justified: If it isn't useful for solving problems, then the simplicity of the interface doesn't matter.
Even if a simpler interface works for certain kinds of problems, be careful when making claims.

Cite other benchmarks, don't do many.

% ==================================================
\section{Appendix}
% ==================================================

\begin{thebibliography}{9}
    \bibitem{gps}
        A. Newell, J. C. Shaw, H. A. Simon
        \textit{Report on a general problem-solving program}
        The Rand corporation, Santa Monica, California, 1958
\end{thebibliography}

\end{document}

### 2017-05-11 papers/paper.tex
Adds logs, improves docs, extends paper

@@
 
-\title{DWave Interface for NP-complete problems}
+\title{Quantum Programming Interface for NP-complete problems}
 \date{05-10-2017}
@@
 
-Programming a quantum annealer to solve certain kinds of NP-complete problems is actually much simpler than one would expect.
+Programming a quantum annealer to solve certain kinds of NP-complete problems is actually very simple.
 Because of the rich software toolchains surrounding the DWave, it is easy to describe problems for the annealer to solve.
-This paper compares various implementations of the Knapsack problem (and lightly covers other NP-complete problems).
+This paper compares various implementations of the Knapsack problem: Classically, using the DWave, and using the IBM Quantum Experience.
+Formal benchmarking is not a direct part of report. Formal benchmarks have been performed in [citations], and will be taken into account in the analysis of this paper.
+[Conclusion recap]
 
@@
 
-...
+The Knapsack problem and other NP-complete problems have immediate real-world applications. 
+However, as the size of an NP-complete problem increases, it becomes very difficult to solve.
+Quantum Computation can allow NP-complete problems to be solved with a polynomial speedup.
+This paper explores different interfaces in the hope of improving the availability of quantum computation, and demonstrating the ease of use of existing interfaces.
+
+\newpage
 
@@
 
+% --------------------------------------------------
+\subsection{Classical Knapsack}
+% --------------------------------------------------
+
+Traditionally, the optimal way to solve the knapsack is through dynamic programming.
+However, the code necessary is potentially difficult to write from scratch:
+
+\lstset{language=Python}
+\begin{lstlisting}
+import functools
+
+def memoize(obj):
+    '''
+    Decorator that caches function calls, allowing dynamic programming.
+    If a function is called twice with the same arguments, the cached result is used.
+
+    obj: function to be cached
+    '''
+    cache = obj.cache = {}
+    @functools.wraps(obj)
+    def memoizer(*args, **kwargs):
+        key = str(args) + str(kwargs)
+        if key not in cache:
+            cache[key] = obj(*args, **kwargs)
+        return cache[key]
+    return memoizer
+
+def knapsack(items, outerConstraints):
+    '''
+    Solve the knapsack problem
+
+    `items`: a sequence of pairs `(value, weight, volume)`, where `value` is
+      a number and `weight` is a non-negative integer.
+
+    `outerConstraints`: a list of numbers representing the maximum values 
+      for each respective constraint
+
+    `return`: a pair whose first element is the sum of values in the most
+    valuable subsequence, and whose second element is the subsequence.
+    '''
+
+    # Return the value of the most valuable subsequence of the first i
+    # elements in items whose constraints are satisfied
+    @memoize
+    def bestvalue(i, constraints): # j is a constraint
+        if i == 0: return 0
+        value, *limiters = items[i - 1]
+        tests = [l > v for l, v in zip(limiters, constraints)]
+        if any(tests): # constraint checking
+            return bestvalue(i - 1, constraints)
+        else:          # maximizing
+            modifications = [v - l for l, v in zip(limiters, constraints)]
+            return max(bestvalue(i - 1, constraints),
+                       bestvalue(i - 1, modifications) + value)
+
+    # Create and modify a copy of
+    k = outerConstraints
+    result = []
+    for i in range(len(items), 0, -1):
+        if bestvalue(i, k) != bestvalue(i - 1, k):
+            result.append(items[i - 1])
+            k = [c - items[i - 1][n + 1] for n, c in enumerate(k)]
+    result.reverse()
+
+    print('Knapsack problem solved classically with {} static evaluations:'.format(len(bestvalue.cache)))
+    choices = [items.index(choice) for choice in result]
+\end{lstlisting}
+
+\newpage
+
+A simpler, naive implementation of the knapsack problem would try every combination of items, choosing the one with the best value that satisfied the constraints.
+
+\lstset{language=Python}
+\begin{lstlisting}
+def naive(items, capacities):
+    selection = []
+    bestval   = 0
+    for comb in powerset(items):
+        if len(comb) > 0:
+            setcaps = setvals(comb)
+            for j, capacity in enumerate(capacities):
+                if j == 0:
+                    if bestval > setcaps[0]:
+                        break
+                else:
+                    if setcaps[j] > capacity:
+                        break
+                if j == len(capacities) - 1: # All constraints satisfied for this set
+                    selection = comb
+    choices = [items.index(choice) for choice in selection]
+    return bestval, selection, choices
+\end{lstlisting}
+
+\newpage
+
+However, a fully polynomial approximation scheme is more accurately comparable to the problem being run on the DWave.
+A FPTAS simplifies the problem given, solving it to withing a margin of error.
+After simplification, FPTAS uses dynamic programming.
+For problems with few variables, the results of FPTAS are very similar to the results of dynamic programming, even if the margin of error is allowed to be high.
+
+\lstset{language=Python}
+\begin{lstlisting}
+def fptas(items, capacities, e=0.1):
+    maxvalue = max(items, key=itemgetter(0))[0]
+    k = e * (maxvalue / len(items))
+    items = [(v/k, *rest) for v, *rest in items]
+    return knapsack(items, capacities)
+\end{lstlisting}
+
+\newpage
+
+Below is output from all three classical solvers on an eight variable knapsack problem:
+
 \begin{verbatim}
-Classical solving:
-    Python:
-        Naive
-        Dynamic Programming
-        Polynomial Approximation
+fptas : 0.0007245789747685194
+{'G', 'B', 'D', 'H', 'E'}
+value is satisfied (70)
+weight is satisfied (60)
+volume is satisfied (55)
+________________________________________________________________________________
 
-Quantum/Simulated solving:
-    Verilog
-    Prolog
-    Grover's (qasm)
+naive : 0.0013742649462074041
+{'G', 'B', 'D', 'H', 'E'}
+value is satisfied (70)
+weight is satisfied (60)
+volume is satisfied (55)
+________________________________________________________________________________
 
-csv problem instance input(s)
+dynamic: 0.0006771821063011885
+{'G', 'B', 'D', 'H', 'E'}
+value is satisfied (70)
+weight is satisfied (60)
+volume is satisfied (55)
+________________________________________________________________________________
 \end{verbatim}
+
+Above 8 variables, the naive implementation times out or returns an incorrect answer.
+
+\newpage
+
+QMASM solving: Verilog and Prolog
+
+\lstset{language=Verilog}
+\begin{lstlisting}
+test
+\end{lstlisting}
+
+\lstset{language=Prolog}
+\begin{lstlisting}
+test
+\end{lstlisting}
+
+\newpage
+
+IBM Quantum experience
 

### 2017-05-11 scripts/solve.py

@@ -7,6 +7,12 @@ from itertools import combinations, chain
 import functools
 
 def memoize(obj):
+    '''
+    Decorator that caches function calls, allowing dynamic programming.
+    If a function is called twice with the same arguments, the cached result is used.
+
+    obj: function to be cached
+    '''
     cache = obj.cache = {}
     @functools.wraps(obj)
     def memoizer(*args, **kwargs):
@@ -20,18 +26,20 @@ def knapsack(items, outerConstraints):
     '''
     Solve the knapsack problem
 
-    `items` is a sequence of pairs `(value, weight, volume)`, where `value` is
-    a number and `weight` is a non-negative integer.
+    `items`: a sequence of pairs `(value, weight, volume)`, where `value` is
+      a number and `weight` is a non-negative integer.
 
+    `outerConstraints`: a list of numbers representing the maximum values 
+      for each respective constraint
 
-    Return a pair whose first element is the sum of values in the most
+    `return`: a pair whose first element is the sum of values in the most
     valuable subsequence, and whose second element is the subsequence.
     '''
 
     # Return the value of the most valuable subsequence of the first i
-    # elements in items whose weights sum to no more than j.
+    # elements in items whose constraints are satisfied
     @memoize
-    def bestvalue(i, constraints): # j is a constraint
+    def bestvalue(i, constraints):
         if i == 0: return 0
         value, *limiters = items[i - 1]
         tests = [l > v for l, v in zip(limiters, constraints)]

### 2017-05-11 prolog/alt_knapsack.pl
Fixes prolog knapsack to use clpfd

@@ -1,0 +1,4 @@
+?- use_module(library(clpfd)).
+knapsack(A, B, C, D, E) :-
+    A * 4 + B * 2 + C * 2 + D + E * 10 #>= 15,
+    A * 12 + B + C * 2 + D + E * 4 #=< 16.

### 2017-05-11 qnp.py

@@ -8,7 +8,7 @@ if __name__ == '__main__':
     args = sys.argv[1:]
     assert len(args) >= 1
     subscript = args[0]
-    showHelp  = subscript in ['-h', '--help']
+    showHelp  = subscript in ['-h', '--help', '--show']
     unknown   = subscript not in subscripts
     if showHelp or unknown:
         print('Subscripts available are:\n    {}'.format(

### 2017-05-11 scripts/__init__.py

@@ -1,9 +1,9 @@
-from .run          import run
-from .create       import create_knapsack, create_map_color
-from .show         import show
-from .rank         import rank 
-from .solve        import solve
-from .verify       import verify
-from .run_qasm     import run_qasm
-from .read_verilog import read_verilog
-from .bool_solve   import bool_solve
+from .run            import run
+from .create         import create_knapsack, create_map_color
+from .show           import show
+from .rank           import rank 
+from .solve          import solve
+from .verify         import verify
+from .run_qasm       import run_qasm
+from .read_verilog   import read_verilog
+from .bool_solve     import bool_solve

### 2017-05-11 scripts/run_qasm.py
Adds four instances of grover's algorithm

@@ -9,7 +9,7 @@ def run_qasm(args):
     assert len(args) >= 1
     filename = args[0]
     if len(args) == 1:
-        containing = ['q0']
+        containing = ['q0', 'q1', 'q2', 'q3', 'q4']
     else:
         containing = args[1:]
     with open(filename, 'r') as qasmfile:

### 2017-05-11 scripts/run_qasm.py
Removes measurement (collapsing)

@@ -17,6 +17,7 @@ def run_qasm(args):
     code = '\n'.join(content)
     print(code)
     qc = QuantumComputer()
+    qc.reset()
     qc.execute(code)
     for c in containing:
         Probability.pretty_print_probabilities(qc.qubits.get_quantum_register_containing(c).get_state())

### 2017-05-12 scripts/__init__.py
Demonstrate IBM API, show Grover results w/script

@@ -7,3 +7,4 @@ from .verify         import verify
 from .run_qasm       import run_qasm
 from .read_verilog   import read_verilog
 from .bool_solve     import bool_solve
+from .quant_exp      import quant_exp

### 2017-05-12 scripts/quant_exp.py

@@ -1,0 +1,20 @@
+from IBMQuantumExperience import IBMQuantumExperience
+
+from pprint import pprint
+
+def quant_exp(args):
+    with open('etc/IBMtoken', 'r') as infile:
+        token = infile.read().replace('\n', '')
+    config = {
+       "url": 'https://quantumexperience.ng.bluemix.net/api'
+    }
+
+    QuantExp = IBMQuantumExperience.IBMQuantumExperience
+    api = QuantExp(token, config)
+    for code in api.get_last_codes():
+        name = code['name']
+        if 'grover' in name.lower():
+            print('IBM Results for{}'.format(name))
+            pprint(code['executions'][-1]['result'])
+            #pprint(code.keys())
+            #pprint(api.get_execution(name))

### 2017-05-12 papers/essay.tex
Adds essay outline

\documentclass{article}

\usepackage{indentfirst}
\usepackage{setspace}
\doublespacing

% ==================================================
% Paper
% ==================================================

\title{Senior Experience Reflective Essay}
\date{05-11-2017}
\author{Lucas Saldyt}

\begin{document}

\maketitle
\pagenumbering{gobble}
\newpage
\pagenumbering{arabic}

% ==================================================
\section{Reflections}
% ==================================================

• What else have you learned about yourself? About your project topic?
• Is the project topic something you are likely to pursue once senior projects are over?
• Without a quiz, paper, test, homework assignment or teacher to motivate you, what has
motivated you to work on your senior project this week? Is it purely getting through the
last graduation requirement, or do you truly enjoy spending time on this project that you
created? Is it hard to motivate yourself to spend time on the project? Write some ideas
about what motivates you.
• If your project were a class and you were the teacher, how would you assess/test/evaluate
your students’ progress, understanding, skill? Would you give a written test based on
knowledge, a hands-on demonstration of skill, or some other evaluation?
• If you made a soundtrack to your senior project, what songs would you include and why?
• Describe a metaphor for this experience. Fill in the blank and elaborate: This experience
has been like...
• What advice would you give next year’s seniors?

% ==================================================
\section{Appendix}
% ==================================================

\end{document}

### 2017-05-12 papers/paper.tex
Adds paper body

--- 2017-05-10 papers/paper.tex
@@
 \usepackage{setspace}
+\usepackage{graphicx}
+\usepackage{pgfplotstable}
 \doublespacing
@@
  \usepackage{listings}
-\usepackage{color}
+  \usepackage{courier}
+ \lstset{
+         basicstyle=\footnotesize\ttfamily, % Standardschrift
+         %numbers=left,               % Ort der Zeilennummern
+         numberstyle=\tiny,          % Stil der Zeilennummern
+         %stepnumber=2,               % Abstand zwischen den Zeilennummern
+         numbersep=5pt,              % Abstand der Nummern zum Text
+         tabsize=2,                  % Groesse von Tabs
+         extendedchars=true,         %
+         breaklines=true,            % Zeilen werden Umgebrochen
+         keywordstyle=\color{red},
+            frame=b,         
+ %        keywordstyle=[1]\textbf,    % Stil der Keywords
+ %        keywordstyle=[2]\textbf,    %
+ %        keywordstyle=[3]\textbf,    %
+ %        keywordstyle=[4]\textbf,   \sqrt{\sqrt{}} %
+         stringstyle=\color{blue}\ttfamily, % Farbe der String
+         showspaces=false,           % Leerzeichen anzeigen ?
+         showtabs=false,             % Tabs anzeigen ?
+         xleftmargin=17pt,
+         framexleftmargin=17pt,
+         framexrightmargin=5pt,
+         framexbottommargin=4pt,
+         %backgroundcolor=\color{lightgray},
+         showstringspaces=false      % Leerzeichen in Strings anzeigen ?        
+ }
+ \lstloadlanguages{% Check Dokumentation for further languages ...
+         %[Visual]Basic
+         %Pascal
+         %C
+         %C++
+         %XML
+         %HTML
+         %Java
+         Python
+ }
+    %\DeclareCaptionFont{blue}{\color{blue}}
 
-\definecolor{dkgreen}{rgb}{0,0.6,0}
-\definecolor{gray}{rgb}{0.5,0.5,0.5}
-\definecolor{mauve}{rgb}{0.58,0,0.82}
-
-\lstset{frame=tb,
-language=C,
-aboveskip=.5mm,
-belowskip=.5mm,
-showstringspaces=false,
-columns=flexible,
-basicstyle={\scriptsize\ttfamily},
-numbers=none,
-numberstyle=\tiny\color{gray},
-keywordstyle=\color{blue},
-commentstyle=\color{dkgreen},
-stringstyle=\color{mauve},
-breaklines=false,
-breakatwhitespace=true,
-tabsize=3
-}
+  %\captionsetup[lstlisting]{singlelinecheck=false, labelfont={blue}, textfont={blue}}
+  \usepackage{caption}
+\DeclareCaptionFont{white}{\color{white}}
+\DeclareCaptionFormat{listing}{\colorbox[cmyk]{0.43, 0.35, 0.35,0.01}{\parbox{\textwidth}{\hspace{15pt}#1#2#3}}}
+\captionsetup[lstlisting]{format=listing,labelfont=white,textfont=white, singlelinecheck=false, margin=0pt, font={bf,footnotesize}}
 
@@
 
-\title{DWave Interface for NP-complete problems}
+\title{Quantum Programming Interfaces for NP-complete problems}
 \date{05-10-2017}
@@
 \newpage
+\tableofcontents
+\newpage
 \pagenumbering{arabic}
@@
 
+% --------------------------------------------------
+\subsection{Classical Knapsack Implementations}
+% --------------------------------------------------
+
+% .................................................. 
+\subsubsection{Naive Implementation}
+% ..................................................
+
+The simplest interface for solving the knapsack problem is a naive python implementation that iterates through every combination of items, and returns the combination with the highest value that satisfies the problem's constraints.
+\lstset{language=Python}
+\lstinputlisting[label=samplecode,caption=Naive Knapsack]{../scripts/naive.py}
+However, the effectiveness of this implementation is limited, and only useful for showing how the code scales with different solvers.
+\newpage
+
+% .................................................. 
+\subsubsection{Dynamic Programming Implementation}
+% ..................................................
+
+Traditionally, the optimal way to solve the knapsack is through dynamic programming.
+However, the code necessary is more difficult to write from scratch:
+
+\lstset{language=Python}
+\lstinputlisting[label=samplecode,caption=Dynamic Programming]{../scripts/dynamic.py}
+\newpage
+
+% .................................................. 
+\subsubsection{Fully Polynomial Approximation Scheme Implementation}
+% ..................................................
+
+However, a fully polynomial approximation scheme is more accurately comparable to the problem being run on the DWave.
+A FPTAS simplifies the problem given, solving it to within a margin of error.
+After simplification, FPTAS uses dynamic programming.
+For problems with few variables, the results of FPTAS are very similar to the results of dynamic programming, even if the margin of error is allowed to be high.
+Notice that the fptas solver calls the dynamic programming solver (with a simpler version of the given problem).
+Even though its implementation appears to be short, it is actually much larger because it includes the dynamic programming code.
+
+\lstset{language=Python}
+\lstinputlisting[label=samplecode,caption=Fully Polynomial Time Approximation Scheme]{../scripts/fptas.py}
+\newpage
+
+% --------------------------------------------------
+\subsection{Quantum Knapsack Implementations}
+% --------------------------------------------------
+
+% .................................................. 
+\subsubsection{DWave Knapsack Implementations : Verilog}
+% ..................................................
+
+While there are many ways of providing problems to the DWave quantum computer (Such as APIs for Python, C++, or Haskell, or an array of Domain Specific Languages), This paper investigates the highest-level implementations possible for the DWave.
+The first way to solve an NP-complete problem on the DWave is to provide a Verilog implementation of a circuit that checks if a solution is correct.
+This provides enough information to generate a Quantum Binary Optimization Problem, which the DWave can perform annealing on.
+Below are a few implementations of verilog circuits and their corresponding circuit images.
+
+\lstset{language=Verilog}
+\lstinputlisting[label=samplecode,caption=Single Constraint Knapsack Problem]{../output/vs/single.v}
+
+\newpage
+\begin{figure}
+  \includegraphics[width=\linewidth]{../output/circuitimages/single.png}
+  \caption{Single constraint circuit representation}
+  \label{fig:single}
+\end{figure}
+To simplify the construction of the Verilog file, one can use additional software:
+\begin{enumerate}
+    \item{QA-Prolog, a compiler from Prolog to Verilog (shown below)}
+    \item{QNP, which includes a script that generates Verilog from a csv file describing the knapsack problem}
+\end{enumerate}
+\newpage
+
+% .................................................. 
+\subsubsection{DWave Knapsack Implementations : Prolog}
+% ..................................................
+
+Using the QA-Prolog software, Prolog can produce similar code to the Verilog shown above.
+The single constraint problem, written in Prolog:
+\lstset{language=Prolog}
+\lstinputlisting[label=samplecode,caption=Single Constraint Knapsack Problem]{../prolog/single.pl}
+
+% .................................................. 
+\subsubsection{DWave Knapsack Implementations : CSV}
+% ..................................................
+
+A csv file, which also compiles to the Verilog shown previously:
+
+\pgfplotstabletypeset[
+    col sep=comma,
+    string type,
+    columns/name/.style={column name=Name, column type={|l}},
+    columns/surname/.style={column name=Surname, column type={|l}},
+    columns/age/.style={column name=Age, column type={|c|}},
+    every head row/.style={before row=\hline,after row=\hline},
+    every last row/.style={after row=\hline},
+    ]{../csvs/single.csv}
+\newpage
+
+% .................................................. 
+\subsubsection{Theoretical IBM Quantum Experience Knapsack Implementations}
+% ..................................................
+
+Quantum Annealing is not the only alternate method of solving the knapsack problem.
+Instead, Universal Gate Quantum Computing offers a polynomial speedup based on Grover's search.
+
+However, the interface for using a Universal Gate Quantum Computer is much different than using a classical computer or the DWave.
+By comparison, the DWave interface may as well be classical, since, as this paper has showed, classical languages can be compiled to annealing problems runnable on the DWave.
+
+The language of Universal Gate Quantum computers is, redundantly, Quantum Gates, which are best expressed in qasm files.
+
+[Grover's Search, etc]
+
+% ==================================================
+\section{Results}
+% ==================================================
+
+Below is output from these three classical solvers on an eight variable knapsack problem:
+
 \begin{verbatim}
-Classical solving:
-    Python:
-        Naive
-        Dynamic Programming
-        Polynomial Approximation
+fptas : 0.0007245789747685194
+{'G', 'B', 'D', 'H', 'E'}
+value is satisfied (70)
+weight is satisfied (60)
+volume is satisfied (55)
+________________________________________________________________________________
 
-Quantum/Simulated solving:
-    Verilog
-    Prolog
-    Grover's (qasm)
+naive : 0.0013742649462074041
+{'G', 'B', 'D', 'H', 'E'}
+value is satisfied (70)
+weight is satisfied (60)
+volume is satisfied (55)
+________________________________________________________________________________
 
-csv problem instance input(s)
+dynamic: 0.0006771821063011885
+{'G', 'B', 'D', 'H', 'E'}
+value is satisfied (70)
+weight is satisfied (60)
+volume is satisfied (55)
+________________________________________________________________________________
 \end{verbatim}
+
+Above 8 variables, the naive implementation times out or returns an incorrect answer.
 

### 2017-05-12 scripts/create.py

@@ -46,7 +46,7 @@ def generate_knapsack(rows, constraints, moduleName, wireSize=32):
     return verilogOutline % (moduleName, 
                             inputs, 
                             inputs,
-                            parameters + '\n' +
+                            parameters + '\n\n    ' +
                             wireAssignments + '\n' +
                             outputAssignments)
 

### 2017-05-12 scripts/dynamic.py

@@ -1,0 +1,63 @@
+import functools
+
+def memoize(obj):
+    '''
+    Decorator that caches function calls, allowing dynamic programming.
+    If a function is called twice with the same arguments, the cached result is used.
+
+    obj: function to be cached
+    '''
+    cache = obj.cache = {}
+    @functools.wraps(obj)
+    def memoizer(*args, **kwargs):
+        key = str(args) + str(kwargs)
+        if key not in cache:
+            cache[key] = obj(*args, **kwargs)
+        return cache[key]
+    return memoizer
+
+def dynamic_knapsack(items, outerConstraints):
+    '''
+    Solve the knapsack problem
+
+    `items`: a sequence of pairs `(value, weight, volume)`, where `value` is
+      a number and `weight` is a non-negative integer.
+
+    `outerConstraints`: a list of numbers representing the maximum values 
+      for each respective constraint
+
+    `return`: a pair whose first element is the sum of values in the most
+    valuable subsequence, and whose second element is the subsequence.
+    '''
+
+    @memoize
+    def bestvalue(i, constraints):
+        '''
+        Return the value of the most valuable subsequence of the first i
+        elements in items whose constraints are satisfied
+        '''
+        if i == 0: return 0
+        value, *limiters = items[i - 1]
+        tests = [l > v for l, v in zip(limiters, constraints)]
+        if any(tests): # constraint checking
+            return bestvalue(i - 1, constraints)
+        else:          # maximizing
+            modifications = [v - l for l, v in zip(limiters, constraints)]
+            return max(bestvalue(i - 1, constraints),
+                       bestvalue(i - 1, modifications) + value)
+
+    k = outerConstraints
+    result = []
+    for i in range(len(items), 0, -1):
+        if bestvalue(i, k) != bestvalue(i - 1, k):
+            result.append(items[i - 1])
+            k = [
+                    c - items[i - 1][n + 1] for n, c in enumerate(k)
+                    ]
+    result.reverse()
+
+    print('Knapsack problem solved classically with {} static evaluations:'.format(len(bestvalue.cache)))
+    choices = [items.index(choice) for choice in result]
+    return bestvalue(len(items), outerConstraints), result, choices
+
+

### 2017-05-12 scripts/naive.py

@@ -1,0 +1,31 @@
+from itertools import chain, combinations
+
+def powerset(iterable):
+    "powerset([1,2,3]) --> () (1,) (2,) (3,) (1,2) (1,3) (2,3) (1,2,3)"
+    s = list(iterable)
+    return chain.from_iterable(combinations(s, r) for r in range(len(s)+1))
+
+def setvals(items):
+    assert(len(items) > 0)
+    setvals = (0,) * len(items[0])
+    for item in items:
+        setvals = tuple(a + b for a, b in zip(setvals, item))
+    return setvals
+
+def naive(items, capacities):
+    selection = []
+    bestval   = 0
+    for comb in powerset(items):
+        if len(comb) > 0:
+            setcaps = setvals(comb)
+            for j, capacity in enumerate(capacities):
+                if j == 0:
+                    if bestval > setcaps[0]:
+                        break
+                else:
+                    if setcaps[j] > capacity:
+                        break
+                if j == len(capacities) - 1: # All constraints satisfied for this set
+                    selection = comb
+    choices = [items.index(choice) for choice in selection]
+    return bestval, selection, choices

### 2017-05-12 scripts/solve.py

@@ -1,69 +1,15 @@
-from .util import read_CSV, verify_set, timedblock, timeout
+from .util    import read_CSV, verify_set, timedblock, timeout
+from .naive   import naive
+from .dynamic import dynamic_knapsack
+from .fptas   import fptas
 
 from functools import reduce
-from operator  import itemgetter, mul
 from itertools import combinations, chain
 
-import functools
-
-def memoize(obj):
-    '''
-    Decorator that caches function calls, allowing dynamic programming.
-    If a function is called twice with the same arguments, the cached result is used.
-
-    obj: function to be cached
-    '''
-    cache = obj.cache = {}
-    @functools.wraps(obj)
-    def memoizer(*args, **kwargs):
-        key = str(args) + str(kwargs)
-        if key not in cache:
-            cache[key] = obj(*args, **kwargs)
-        return cache[key]
-    return memoizer
-
-def knapsack(items, outerConstraints):
-    '''
-    Solve the knapsack problem
-
-    `items`: a sequence of pairs `(value, weight, volume)`, where `value` is
-      a number and `weight` is a non-negative integer.
-
-    `outerConstraints`: a list of numbers representing the maximum values 
-      for each respective constraint
-
-    `return`: a pair whose first element is the sum of values in the most
-    valuable subsequence, and whose second element is the subsequence.
-    '''
-
-    # Return the value of the most valuable subsequence of the first i
-    # elements in items whose constraints are satisfied
-    @memoize
-    def bestvalue(i, constraints):
-        if i == 0: return 0
-        value, *limiters = items[i - 1]
-        tests = [l > v for l, v in zip(limiters, constraints)]
-        if any(tests): # constraint checking
-            return bestvalue(i - 1, constraints)
-        else:          # maximizing
-            modifications = [v - l for l, v in zip(limiters, constraints)]
-            return max(bestvalue(i - 1, constraints),
-                       bestvalue(i - 1, modifications) + value)
-
-    k = outerConstraints
-    result = []
-    for i in range(len(items), 0, -1):
-        if bestvalue(i, k) != bestvalue(i - 1, k):
-            result.append(items[i - 1])
-            k = [
-                    c - items[i - 1][n + 1] for n, c in enumerate(k)
-                    ]
-    result.reverse()
-
[…]

### 2017-05-13 scripts/create.py
Adds Grover comparison logic problems

@@ -86,7 +86,6 @@ def creator(f):
                 outfile.write(verilog)
             a, b = to_output(bname)
             resulta = interpret_output(a)
-            resulta = [item for item in resulta if '$' not in item[0]]
             resultb = interpret_output(b)
             print('minizinc')
             print(resulta)

### 2017-05-13 scripts/run.py

@@ -2,7 +2,7 @@
 import subprocess, shutil, sys, os
 from collections import OrderedDict
 
-from .util import basename, timedblock
+from .util import basename, timedblock, verify_set, to_set
 
 def runc(command, filename=None, checkOut=False):
     if filename is None:
@@ -40,8 +40,6 @@ def get_named_bits(output):
     return named_bits
 
 def interpret_output(output):
-    toReturn = []
-
     namedBits = get_named_bits(output)
 
     d = OrderedDict()
@@ -55,7 +53,9 @@ def interpret_output(output):
                 d[prename] = (2 ** index * bit)
         else:
             d[name] = bit
-    return list(d.items())
+    result = list(d.items())
+    comp = lambda item : '$' not in item[0] and item[0] != 'Name(s)'
+    return [item for item in result if comp(item)]
 
 def to_output(filename):
     runc('verilator --lint-only -Wall @.v', filename)
@@ -84,6 +84,8 @@ def run(args):
             a, b = to_output(bname)
             resulta = interpret_output(a)
             resultb = interpret_output(b)
+
+            print(to_set(resulta), to_set(resultb))
         finally:
             pass
     return resulta

### 2017-05-13 scripts/util.py

@@ -54,6 +54,12 @@ def read_CSV(args):
         csvInput = [line for line in infile]
         return _read_CSV_input(csvInput)
 
+def to_set(results):
+    results = [t[0].split('.')[-1] for t in results if t[1] == 1]
+    selection = {item for item in results if item != 'valid'}
+    print(selection)
+    return selection
+
 def verify_set(args, s):
     rows, constraints = read_CSV(args)
     initial = [0 for _ in range(len(list(rows.values())[0]))]

### 2017-05-13 scripts/verify.py

@@ -1,6 +1,6 @@
 from .create import create_knapsack
 from .solve  import solve
-from .util   import read_CSV, verify_set
+from .util   import read_CSV, verify_set, to_set
 
 import os
 
@@ -14,12 +14,6 @@ def overview(args):
         comp = 'greater than or equal to' if m == 'min' else 'less than or equal to'
         print('{} is {} {}'.format(name, comp, value))
     print('')
-
-def to_set(results):
-    results = [t[0].split('.')[-1] for t in results if t[1] == 1]
-    selection = {item for item in results if item != 'valid'}
-    print(selection)
-    return selection
 
 def verify(args):
     overview(args)

### 2017-05-16 scripts/dynamic.py
Adds better classical analysis options

@@ -56,7 +56,7 @@ def dynamic_knapsack(items, outerConstraints):
                     ]
     result.reverse()
 
-    print('Knapsack problem solved classically with {} static evaluations:'.format(len(bestvalue.cache)))
+    #print('Knapsack problem solved classically with {} static evaluations:'.format(len(bestvalue.cache)))
     choices = [items.index(choice) for choice in result]
     return bestvalue(len(items), outerConstraints), result, choices
 

### 2017-05-16 scripts/run.py

@@ -68,11 +68,14 @@ def to_output(filename):
                        ' --format=qbsolv --pin="@.valid := true"', 
                        filename,
                        checkOut=True)
+    '''
     with timedblock('minizinc'):
         zincOut = runc('qmasm -O -v output/qmasms/@.qmasm --run' + 
                        ' --format=minizinc --pin="@.valid := true"', 
                        filename,
                        checkOut=True)
+    '''
+    zincOut = ''
     return zincOut, quboOut
 
 def run(args):
@@ -82,13 +85,13 @@ def run(args):
             shutil.copy(filename, bname + '.v')
         try:
             a, b = to_output(bname)
-            resulta = interpret_output(a)
+            #resulta = interpret_output(a)
             resultb = interpret_output(b)
 
-            print(to_set(resulta), to_set(resultb))
+            #print(to_set(resulta), to_set(resultb))
         finally:
             pass
-    return resulta
+    return resultb
 
 if __name__ == '__main__':
     run(sys.argv[1:])

### 2017-05-16 scripts/solve.py

@@ -12,13 +12,18 @@ https://www.cs.cmu.edu/afs/cs/academic/class/15854-f05/www/scribe/lec10.pdf
 '''
 
 def solve(args):
+    if len(args) > 1:
+        iterations = int(args[1])
+        args = args[:1]
+    else:
+        iterations = 1
     rows, constraintTuples = read_CSV(args)
     items = [tuple(item) for item in rows.values()]
     constraints = []
     for c in constraintTuples[1:]:
         constraints.append(int(c[2]))
     keys = list(rows.keys())
-    def test_algo(algo, iterations=1, maxTime=3, **kwargs):
+    def test_algo(algo, iterations=iterations, maxTime=3, **kwargs):
         selection = set()
         try:
             with timeout(maxTime):
@@ -26,6 +31,7 @@ def solve(args):
                     for i in range(iterations):
                         _, _, choices = algo(items, constraints, **kwargs)
                 selection = {keys[i] for i in choices}
+                print('({} iterations, timing=time.perf_time())'.format(iterations))
                 print(selection)
                 verify_set(args, selection)
         except TimeoutError as e:
@@ -33,9 +39,9 @@ def solve(args):
         print('\n{}\n'.format('_' * 80))
         return selection
 
-    test_algo(fptas)
+    #test_algo(fptas)
     #test_algo(greedy)
-    test_algo(naive)
+    #test_algo(naive)
     selection = test_algo(dynamic_knapsack)
     return selection
 

### 2017-05-16 scripts/run.py
Adds robust benchmarking options for classical

@@ -68,14 +68,11 @@ def to_output(filename):
                        ' --format=qbsolv --pin="@.valid := true"', 
                        filename,
                        checkOut=True)
-    '''
     with timedblock('minizinc'):
         zincOut = runc('qmasm -O -v output/qmasms/@.qmasm --run' + 
                        ' --format=minizinc --pin="@.valid := true"', 
                        filename,
                        checkOut=True)
-    '''
-    zincOut = ''
     return zincOut, quboOut
 
 def run(args):
@@ -85,13 +82,13 @@ def run(args):
             shutil.copy(filename, bname + '.v')
         try:
             a, b = to_output(bname)
-            #resulta = interpret_output(a)
+            resulta = interpret_output(a)
             resultb = interpret_output(b)
 
-            #print(to_set(resulta), to_set(resultb))
+            print(to_set(resulta), to_set(resultb))
         finally:
             pass
-    return resultb
+    return resulta
 
 if __name__ == '__main__':
     run(sys.argv[1:])

### 2017-05-16 scripts/solve.py

@@ -39,7 +39,7 @@ def solve(args):
         print('\n{}\n'.format('_' * 80))
         return selection
 
-    #test_algo(fptas)
+    test_algo(fptas, e=.1)
     #test_algo(greedy)
     #test_algo(naive)
     selection = test_algo(dynamic_knapsack)

### 2017-05-16 papers/paper.tex
WIP School suitable paper draft

@@
 
+This report explores different programming interfaces for solving NP-complete problems.
+Different classical algorithms are compared to the interfaces for both the DWave quantum annealer and the IBM Quantum Experience Computer.
+This paper does not implement a direct benchmark between IBM and DWave.
+Instead, it describes the programming interface for each, and relies on other publications for benchmarks, which are hard to do correctly.
+
 Programming a quantum annealer to solve certain kinds of NP-complete problems is actually very simple.
 Because of the rich software toolchains surrounding the DWave, it is easy to describe problems for the annealer to solve.
-This paper compares various implementations of the Knapsack problem: Classically, using the DWave, and using the IBM Quantum Experience.
-Formal benchmarking is not a direct part of report. Formal benchmarks have been performed in [citations], and will be taken into account in the analysis of this paper.
-[Conclusion recap]
+However, DWave has limitations in the size of problems it can run and how quickly it can run them.
+So, DWave (and quantum annealing in general), despite having a useable interface, still needs many improvements before it will be useful on real problems.
+
+IBM does not allow the same level of abstraction as DWave, but has other benefits.
+If the interface for programming a Universal Gate Quantum Computer improves, IBM will be a strong option for solving NP-complete problems quickly.
+
+While Quantum Computation has proved useful on fabricated problems, there is still a long time before it has a true impact on real world problem solving.
 
@@
 This paper explores different interfaces in the hope of improving the availability of quantum computation, and demonstrating the ease of use of existing interfaces.
-
 \newpage
@@
 % --------------------------------------------------
+
+Firstly, this paper shows three classical implementations of the Knapsack problem, each written in Python.
+The purpose of this is to make it clear how classical interfaces look compared to quantum interfaces.
 
@@
 
+While there are many ways of providing problems to the DWave quantum computer (Such as APIs for Python, C++, or Haskell, or an array of Domain Specific Languages), This paper investigates the highest-level implementations possible for the DWave.
+
 % .................................................. 
@@
 
-While there are many ways of providing problems to the DWave quantum computer (Such as APIs for Python, C++, or Haskell, or an array of Domain Specific Languages), This paper investigates the highest-level implementations possible for the DWave.
-The first way to solve an NP-complete problem on the DWave is to provide a Verilog implementation of a circuit that checks if a solution is correct.
+The first way to solve an NP-complete problem on the DWave is to provide a Verilog implementation of a classical "oracle" circuit that checks if a solution is correct.
 This provides enough information to generate a Quantum Binary Optimization Problem, which the DWave can perform annealing on.
-Below are a few implementations of verilog circuits and their corresponding circuit images.
+Below is a Verilog circuit, its corresponding image , and its corresponding image after problem reduction (to boolean satisfiability).
 
@@
 \newpage
-\begin{figure}
+\begin{figure}[h!]
   \includegraphics[width=\linewidth]{../output/circuitimages/single.png}
@@
 \end{figure}
+\begin{figure}[h!]
+  \includegraphics[width=\linewidth]{../output/circuitimages/single_opt.png}
+  \caption{Optimized single constraint circuit representation}
+  \label{fig:opt_single}
+\end{figure}
+\newpage
+
 To simplify the construction of the Verilog file, one can use additional software:
@@
 \end{enumerate}
+
 \newpage
@@
 
-The language of Universal Gate Quantum computers is, redundantly, Quantum Gates, which are best expressed in qasm files.
+The language of Universal Gate Quantum computers is Quantum Gates, which are expressed in qasm files.
+While a qasm file describing Grover's search is potentially short, it requires expert knowledge to write, as each line of code represents multiplying a vector of complex numbers by a matrix of complex numbers.
+Like with the DWave interface, the code will look different for each problem, as well as scaling with the problem itself.
+An advantage to the classical interface is that the code can stay the same even when the problem changes.
 
-[Grover's Search, etc]
+\lstset{language=C}
+\lstinputlisting[label=samplecode,caption=Grover's search on a two-variable problem]{../qasms/grover_n2_a01.qasm}
 
@@
 
-Below is output from these three classical solvers on an eight variable knapsack problem:
+A description of the five variable knapsack problem run below:
+\begin{verbatim}
+Given the following items:
+Name : [value, weight, volume]
+A    : [4,     28,      27]
+B    : [8,      8,      27]
+C    : [1,     27,       4]
+D    : [20,    18,       4]
+E    : [10,    27,       1]
+Choose a set, such that:
+value is greater than or equal to 30
+weight is less than or equal to 50
+volume is less than or equal to 50
+\end{verbatim}
+
+Below is output from these three classical solvers on a five variable knapsack problem:
 
 \begin{verbatim}
-fptas : 0.0007245789747685194
-{'G', 'B', 'D', 'H', 'E'}
-value is satisfied (70)
-weight is satisfied (60)
-volume is satisfied (55)
+fptas : 0.00019335599972691853
+{'D', 'E'}
+value is satisfied (30)
+weight is satisfied (45)
+volume is satisfied (5)
 ________________________________________________________________________________
 
-naive : 0.0013742649462074041
-{'G', 'B', 'D', 'H', 'E'}
-value is satisfied (70)
-weight is satisfied (60)
-volume is satisfied (55)
+naive : 0.00013976199988974258
+{'D', 'E'}
+value is satisfied (30)
+weight is satisfied (45)
+volume is satisfied (5)
 ________________________________________________________________________________
 
-dynamic: 0.0006771821063011885
-{'G', 'B', 'D', 'H', 'E'}
-value is satisfied (70)
-weight is satisfied (60)
-volume is satisfied (55)
+dynamic_knapsack : 0.00015341899961640593
+{'D', 'E'}
+value is satisfied (30)
+weight is satisfied (45)
+volume is satisfied (5)
 ________________________________________________________________________________
@@
 
-Above 8 variables, the naive implementation times out or returns an incorrect answer.
+DWave's annealing successfully solves the 5 variable knapsack problem as well:
+
+\begin{verbatim}
+Submitting the problem to the DW2X solver.
+
+[...]
+
+Timing information:
+
+    Measurement                    Value (us)
+    ------------------------------ ----------
+    total_real_time                    199315
+    anneal_time_per_run                    20
+    post_processing_overhead_time        4406
+    qpu_sampling_time                  181780
+    readout_time_per_run                  141
+    qpu_delay_time_per_sample              21
+    qpu_anneal_time_per_sample             20
+    total_post_processing_time           4406
+    qpu_programming_time                15160
+    run_time_chip                      181780
+    qpu_access_time                    199315
+    qpu_readout_time_per_sample           141
+
+Number of solutions found:
+
+        75 total
+        33 with no broken chains or broken pins
+         1 at minimal energy
+         1 excluding duplicate variable assignments
+
+Solution #1 (energy = -26.00, tally = 56):
+
+    Name                Spin  Boolean
+    ------------------  ----  --------
+    harder_multi.A        -1  False  
+    harder_multi.B        -1  False  
+    harder_multi.C        -1  False  
+    harder_multi.D        +1  True   
+    harder_multi.E        +1  True   
+    harder_multi.valid    +1  True
+
+{'D', 'E'}
+\end{verbatim}
+
+This report does not include a five variable problem being run on IBM's topology.
 
@@
 
-Which interface is simplest? Easiest to use?
-Simple interface must be justified: If it isn't useful for solving problems, then the simplicity of the interface doesn't matter.
-Even if a simpler interface works for certain kinds of problems, be careful when making claims.
+Quantum Computers currently do not help solve non trivial real world problems in an advantageous way.
 
-Cite other benchmarks, don't do many.
+DWave has superior interface, but has more hardware improvements to make.
+
+Both IBM and DWave need hardware improvements, but DWave needs more.
+
+IBM Interface is only usable for specialists, not layprogrammers
 
@@
 \begin{thebibliography}{9}
-    \bibitem{gps}
+    \bibitem{problem-solving-paper}
         A. Newell, J. C. Shaw, H. A. Simon

### 2017-05-16 scripts/greedy.py
Adds greedy redux algo, 10x faster than dynamic

@@ -1,0 +1,32 @@
+from operator  import mul
+from functools import reduce
+
+def greedy(items, capacities):
+    rank   = lambda item : item[0] / max(1, (reduce(mul, item[1:], 1)))
+    sitems = sorted(items, key=rank, reverse=True)
+
+    selection = []
+    setcaps = (0,) * len(capacities)
+    breakOuter = False
+
+    for i, item in enumerate(sitems):
+        if breakOuter:
+            break
+        for j, capacity in enumerate(capacities):
+            if j != 0:
+                if setcaps[j] + item[j] >= capacity:
+                    breakOuter=True
+                    break
+            if j == len(capacities) - 1:
+                setcaps = tuple(a + b for a, b in zip(setcaps, item))
+
+    bestval = 0
+    if all(a <= b for a, b in zip(sitems[i][1:], capacities[1:])):
+        if sitems[i][0] > bestval:
+            selection = [sitems[i]]
+    value = sum(item[0] for item in sitems[:1])
+    if value > bestval:
+        selection = sitems[:i]
+        
+    choices = [items.index(choice) for choice in selection]
+    return bestval, selection, choices

### 2017-05-16 scripts/quant_exp.py

@@ -12,9 +12,12 @@ def quant_exp(args):
     QuantExp = IBMQuantumExperience.IBMQuantumExperience
     api = QuantExp(token, config)
     for code in api.get_last_codes():
+        pprint(code)
+        '''
         name = code['name']
         if 'grover' in name.lower():
             print('IBM Results for{}'.format(name))
             pprint(code['executions'][-1]['result'])
             #pprint(code.keys())
             #pprint(api.get_execution(name))
+        '''

### 2017-05-16 scripts/solve.py

@@ -2,8 +2,8 @@ from .util    import read_CSV, verify_set, timedblock, timeout
 from .naive   import naive
 from .dynamic import dynamic_knapsack
 from .fptas   import fptas
+from .greedy  import greedy
 
-from functools import reduce
 from itertools import combinations, chain
 
 '''
@@ -40,29 +40,7 @@ def solve(args):
         return selection
 
     test_algo(fptas, e=.1)
-    #test_algo(greedy)
+    test_algo(greedy)
     #test_algo(naive)
     selection = test_algo(dynamic_knapsack)
     return selection
-
-
-'''
-def greedy(items, capacities):
-    rank   = lambda item : item[0] / max(1, (reduce(mul, item[1:], 1)))
-    sitems = sorted(items, key=rank)
-
-    selection = []
-    bestval = 0
-    setcaps = (0,) * len(capacities)
-    for i, item in enumerate(sitems):
-        setcaps = tuple(a + b for a, b in zip(setcaps, item))
-        for j, capacity in enumerate(capacities):
-            if j != 0:
-                if setcaps[j] > capacity:
-
-                    break
-        print(setcaps)
-        
-    choices = [items.index(choice) for choice in selection]
-    return bestval, selection, choices
-'''

### 2017-05-16 scripts/naive.py
Fixes off-by-one error in naive algo

@@ -18,14 +18,11 @@ def naive(items, capacities):
     for comb in powerset(items):
         if len(comb) > 0:
             setcaps = setvals(comb)
-            for j, capacity in enumerate(capacities):
-                if j == 0:
-                    if bestval > setcaps[0]:
+            if bestval < setcaps[0]:
+                for j, capacity in enumerate(capacities):
+                    if setcaps[j + 1] > capacity:
                         break
-                else:
-                    if setcaps[j] > capacity:
-                        break
-                if j == len(capacities) - 1: # All constraints satisfied for this set
-                    selection = comb
+                    if j == len(capacities) - 1: # All constraints satisfied for this set
+                        selection = comb
     choices = [items.index(choice) for choice in selection]
     return bestval, selection, choices

### 2017-05-16 scripts/solve.py

@@ -41,6 +41,6 @@ def solve(args):
 
     test_algo(fptas, e=.1)
     test_algo(greedy)
-    #test_algo(naive)
+    test_algo(naive)
     selection = test_algo(dynamic_knapsack)
     return selection

### 2017-05-16 scripts/solve.py
Adds classical algo results for 1,000,000 iters

@@ -23,7 +23,7 @@ def solve(args):
     for c in constraintTuples[1:]:
         constraints.append(int(c[2]))
     keys = list(rows.keys())
-    def test_algo(algo, iterations=iterations, maxTime=3, **kwargs):
+    def test_algo(algo, iterations=iterations, maxTime=1, **kwargs):
         selection = set()
         try:
             with timeout(maxTime):

### 2017-05-16 scripts/greedy.py
Adds disclaimer about greedy algo

@@ -2,6 +2,10 @@ from operator  import mul
 from functools import reduce
 
 def greedy(items, capacities):
+    '''
+    Currently undefined on problems with more than two constraints
+    (ie a problem with value, weight, and volume)
+    '''
     rank   = lambda item : item[0] / max(1, (reduce(mul, item[1:], 1)))
     sitems = sorted(items, key=rank, reverse=True)
 

### 2017-05-16 scripts/solve.py
Adds var5 results, 1,000,000 iterations

@@ -23,7 +23,7 @@ def solve(args):
     for c in constraintTuples[1:]:
         constraints.append(int(c[2]))
     keys = list(rows.keys())
-    def test_algo(algo, iterations=iterations, maxTime=1, **kwargs):
+    def test_algo(algo, iterations=iterations, maxTime=1000, **kwargs):
         selection = set()
         try:
             with timeout(maxTime):
@@ -40,7 +40,7 @@ def solve(args):
         return selection
 
     test_algo(fptas, e=.1)
-    test_algo(greedy)
+    #test_algo(greedy)
     test_algo(naive)
     selection = test_algo(dynamic_knapsack)
     return selection

### 2017-05-16 papers/paper.tex
Adds Paper draft

@@
 Different classical algorithms are compared to the interfaces for both the DWave quantum annealer and the IBM Quantum Experience Computer.
-This paper does not implement a direct benchmark between IBM and DWave.
-Instead, it describes the programming interface for each, and relies on other publications for benchmarks, which are hard to do correctly.
 
-Programming a quantum annealer to solve certain kinds of NP-complete problems is actually very simple.
 Because of the rich software toolchains surrounding the DWave, it is easy to describe problems for the annealer to solve.
 However, DWave has limitations in the size of problems it can run and how quickly it can run them.
-So, DWave (and quantum annealing in general), despite having a useable interface, still needs many improvements before it will be useful on real problems.
+DWave (and quantum annealing in general), despite having a useable interface, still needs many improvements before it will be useful on real problems.
 
-IBM does not allow the same level of abstraction as DWave, but has other benefits.
+IBM does not allow the same level of abstraction as DWave, but has been proven asymptotically faster than classical computing.
+However, it is limited to five qubits, effectively making it limited to a five variable problem if the problem is run in full.
 If the interface for programming a Universal Gate Quantum Computer improves, IBM will be a strong option for solving NP-complete problems quickly.
@@
 However, as the size of an NP-complete problem increases, it becomes very difficult to solve.
-Quantum Computation can allow NP-complete problems to be solved with a polynomial speedup.
-This paper explores different interfaces in the hope of improving the availability of quantum computation, and demonstrating the ease of use of existing interfaces.
+Quantum Computation can allow NP-complete problems to be solved more quickly.
+Quantum Annealing may eventually allow for the same.
+This paper explores different interfaces in the hope of improving the availability of quantum problem solving, and demonstrating the ease of use of existing interfaces.
 \newpage
@@
 
-Firstly, this paper shows three classical implementations of the Knapsack problem, each written in Python.
+Firstly, this paper shows classical implementations of the Knapsack problem, each written in Python.
 The purpose of this is to make it clear how classical interfaces look compared to quantum interfaces.
@@
 \lstinputlisting[label=samplecode,caption=Fully Polynomial Time Approximation Scheme]{../scripts/fptas.py}
+\newpage
+
+% .................................................. 
+\subsubsection{Greedy hueristic solver}
+% ..................................................
+
+The current implementation of the greedy algorithm only works on single constraint problems, but is very fast:
+
+\lstset{language=Python}
+\lstinputlisting[label=samplecode,caption=Greedy Knapsack Algorithm]{../scripts/greedy.py}
 \newpage
@@
     ]{../csvs/single.csv}
+
 \newpage
@@
 
-The language of Universal Gate Quantum computers is Quantum Gates, which are expressed in qasm files.
+The language of Universal Gate Quantum computers usually is Quantum Gates, which are expressed in qasm files.
 While a qasm file describing Grover's search is potentially short, it requires expert knowledge to write, as each line of code represents multiplying a vector of complex numbers by a matrix of complex numbers.
@@
 
+Note that this code shown solves a two variable version of the knapsack problem.
+
 \lstset{language=C}
 \lstinputlisting[label=samplecode,caption=Grover's search on a two-variable problem]{../qasms/grover_n2_a01.qasm}
+
+% .................................................. 
+\subsubsection{Alternate Gate Model Languages}
+% ..................................................
+
+In addition to qasm, QML or QCL can be used to program a gate model quantum computer.
+[...]
 
@@
 
-Below is output from these three classical solvers on a five variable knapsack problem:
+Below is output from the classical solvers on a five variable knapsack problem:
+(Run with 1,000,000 iterations)
 
 \begin{verbatim}
-fptas : 0.00019335599972691853
-{'D', 'E'}
+lucas@qed:~/projects/lanl/qnp$ ./qnp solve csvs/var5_multi.csv 1000000
+['csvs/var5_multi.csv', '1000000']
+fptas : 120.80939865000255
+(1000000 iterations, timing=time.perf_time())
+{'E', 'D'}
 value is satisfied (30)
@@
 
-naive : 0.00013976199988974258
-{'D', 'E'}
+naive : 107.68942248700478
+(1000000 iterations, timing=time.perf_time())
+{'E', 'D'}
 value is satisfied (30)
@@
 
-dynamic_knapsack : 0.00015341899961640593
-{'D', 'E'}
+dynamic_knapsack : 114.03447730200423
+(1000000 iterations, timing=time.perf_time())
+{'E', 'D'}
 value is satisfied (30)
@@
 
+\textit{SECTION IN PROGRESS}
+
 Quantum Computers currently do not help solve non trivial real world problems in an advantageous way.
 
-DWave has superior interface, but has more hardware improvements to make.
+DWave currently has a superior interface, but has not proven an asymptotic advantage.
 
-Both IBM and DWave need hardware improvements, but DWave needs more.
-
-IBM Interface is only usable for specialists, not layprogrammers
+The IBM Interface is less usable for layprogrammers, but the gate model has been theoretically proven faster than the classical model of computation.
 
@@
 \begin{thebibliography}{9}
-    \bibitem{problem-solving-paper}
-        A. Newell, J. C. Shaw, H. A. Simon
-        \textit{Report on a general problem-solving program}
-        The Rand corporation, Santa Monica, California, 1958
+    \bibitem{x}
+        Authors
+        \textit{Title}
+        Pub, Loc, Date
 \end{thebibliography}

### 2017-05-16 scripts/__init__.py
Adds QCL Hello World example

@@ -1,10 +1,11 @@
-from .run            import run
-from .create         import create_knapsack, create_map_color
-from .show           import show
-from .rank           import rank 
-from .solve          import solve
-from .verify         import verify
-from .run_qasm       import run_qasm
-from .read_verilog   import read_verilog
-from .bool_solve     import bool_solve
-from .quant_exp      import quant_exp
+from .run          import run
+from .run_qasm     import run_qasm
+from .run_qcl      import run_qcl
+from .create       import create_knapsack, create_map_color
+from .show         import show
+from .rank         import rank 
+from .solve        import solve
+from .verify       import verify
+from .read_verilog import read_verilog
+from .bool_solve   import bool_solve
+from .quant_exp    import quant_exp

### 2017-05-16 scripts/create.py
Adds iterations support for simulated annealers

@@ -4,7 +4,7 @@ from math import log
 from functools import wraps
 
 from .run import runc, to_output, interpret_output
-from .util import read_CSV, suppress_output, basename, verify_set
+from .util import read_CSV, suppress_output, basename, verify_set, get_iterations
 
 verilogOutline = """
 module %s (%s, valid);
@@ -84,7 +84,8 @@ def creator(f):
             verilog = f(args)
             with open(outputfile, 'w') as outfile:
                 outfile.write(verilog)
-            a, b = to_output(bname)
+            iterations = get_iterations(args)
+            a, b = to_output(bname, iterations)
             resulta = interpret_output(a)
             resultb = interpret_output(b)
             print('minizinc')
@@ -92,7 +93,13 @@ def creator(f):
             print('qbsolv')
             print(resultb)
             if resulta != resultb:
-                print('{} (from minizinc) is not equal to {} (from qbsolv)'.format(resulta, resultb))
+                print('    "{}"\n    (from minizinc) is not equal to\n    "{}"\n    (from qbsolv):'.format(resulta, resultb))
+                '''
+                print('minizinc output:')
+                print(a)
+                print('qbsolv output:')
+                print(b)
+                '''
             return resulta, resultb
         finally:
             with suppress_output():
@@ -105,7 +112,7 @@ def create_knapsack(args):
     inputfile = args[0]
     bname = basename(inputfile)
     rows, constraints = read_CSV(args)
-    wireSize = max_int(rows) if len(args) == 1 else int(args[1])
+    wireSize = max_int(rows)
     print('Wire size selected as {}'.format(wireSize))
     return generate_knapsack(rows, constraints, bname, wireSize=wireSize)
 

### 2017-05-16 scripts/run.py

@@ -2,19 +2,19 @@
 import subprocess, shutil, sys, os
 from collections import OrderedDict
 
-from .util import basename, timedblock, verify_set, to_set
+from .util import basename, timedblock, verify_set, to_set, get_iterations
 
 def runc(command, filename=None, checkOut=False):
     if filename is None:
         assert '@' not in command
         filename = ''
     command = command.replace('@', filename)
-    print(command + ':')
     if checkOut:
         try:
             output = subprocess.check_output(command, shell=True, stderr=subprocess.STDOUT)
             return output.decode('unicode_escape')
         except subprocess.CalledProcessError as e:
+            print(command + ':')
             print(e.output)
             raise
     else:
@@ -54,40 +54,45 @@ def interpret_output(output):
         else:
             d[name] = bit
     result = list(d.items())
-    comp = lambda item : '$' not in item[0] and item[0] != 'Name(s)'
+    comp = lambda item : '$' not in item[0] and item[0] != 'Name(s)' and 'valid' not in item[0]
     return [item for item in result if comp(item)]
 
-def to_output(filename):
+def to_output(filename, iterations=1):
     runc('verilator --lint-only -Wall @.v', filename)
     runc('yosys -q @.v scripts/synth.ys -b edif -o output/edifs/@.edif', filename)
     shutil.move('output/vs/__opt__.v', 'output/vs/opt_{}.v'.format(filename))
     runc('edif2qmasm output/edifs/@.edif > output/qmasms/@.qmasm', filename)
+    runc('qmasm --format=qbsolv -o output/qubos/@.qubo --pin="@.valid:= true" output/qmasms/@.qmasm', filename)
     # Requires verilog modulename matches filename, bool output is named 'valid'
     with timedblock('qbsolv'):
-        quboOut = runc('qmasm -O -v output/qmasms/@.qmasm --run' + 
-                       ' --format=qbsolv --pin="@.valid := true"', 
-                       filename,
-                       checkOut=True)
+        for i in range(iterations):
+            quboOut = runc('qmasm -O -v output/qmasms/@.qmasm --run' + 
+                           ' --format=qbsolv --pin="@.valid := true"', 
+                           filename,
+                           checkOut=True)
     with timedblock('minizinc'):
-        zincOut = runc('qmasm -O -v output/qmasms/@.qmasm --run' + 
-                       ' --format=minizinc --pin="@.valid := true"', 
-                       filename,
-                       checkOut=True)
+        for i in range(iterations):
[…]

### 2017-05-16 scripts/solve.py

@@ -1,4 +1,4 @@
-from .util    import read_CSV, verify_set, timedblock, timeout
+from .util    import read_CSV, verify_set, timedblock, timeout, get_iterations
 from .naive   import naive
 from .dynamic import dynamic_knapsack
 from .fptas   import fptas
@@ -12,18 +12,14 @@ https://www.cs.cmu.edu/afs/cs/academic/class/15854-f05/www/scribe/lec10.pdf
 '''
 
 def solve(args):
-    if len(args) > 1:
-        iterations = int(args[1])
-        args = args[:1]
-    else:
-        iterations = 1
+    iterations = get_iterations(args)
     rows, constraintTuples = read_CSV(args)
     items = [tuple(item) for item in rows.values()]
     constraints = []
     for c in constraintTuples[1:]:
         constraints.append(int(c[2]))
     keys = list(rows.keys())
-    def test_algo(algo, iterations=iterations, maxTime=1000, **kwargs):
+    def test_algo(algo, iterations=iterations, maxTime=1, **kwargs):
         selection = set()
         try:
             with timeout(maxTime):
@@ -40,7 +36,8 @@ def solve(args):
         return selection
 
     test_algo(fptas, e=.1)
-    #test_algo(greedy)
+    if len(constraints) == 1:
+        test_algo(greedy)
     test_algo(naive)
     selection = test_algo(dynamic_knapsack)
     return selection

### 2017-05-16 scripts/util.py

@@ -25,6 +25,14 @@ def suppress_output():
             sys.stdout = sys.__stdout__
             sys.stderr = sys.__stderr__
 
+def get_iterations(args):
+    if len(args) > 1:
+        i = int(args[1])
+        assert(i > 0)
+        return i
+    else:
+        return 1
+
 # Read rows and constraints from csvInput
 # rows is a list of the form [(A, [4, 12]), (B, [2, 1])]
 # constraints is a list of the form [('min', 'value', '15'), ('max', 'weight', '16')]

### 2017-05-16 papers/paper.tex
Adds bibliography

@@
 \begin{thebibliography}{9}
-    \bibitem{x}
-        Authors
-        \textit{Title}
-        Pub, Loc, Date
+    \bibitem{}
+        Pakin, Scott
+        \textit{Performing Fully Parallel Constraint Logic Programming on a Quantum Annealer}
+        Cambridge University Press, 2017
+    \bibitem{}
+        Grover, Lok K.
+        \textit{A fast quantum mechanical algorithm for database search}
+        Proceedings of 28th Symp Theory of Computing, 1996
+    \bibitem{}
+        John Wright
+        \textit{Lecture 4: Grover's Algorithm}
+        Carnegie Mellon University, 2015
+    \bibitem{}
+        Arvind, V., Schuler, Rainer
+        \textit{The Quantum Query Complexity of 0-1 Knapsack and Associated Claw Problems}
+        Archiv, Accessed 2017
+    \bibitem{}
+        Dahl, E. D.
+        \textit{Programming With the D-Wave: Map Coloring Problem}
+        D-Wave systems, 2013
+    \bibitem{}
+        Ines Dutra
+        \textit{Constraint Logic Programming: a short tutorial}
+        University of Porto, 2010
+    \bibitem{}
+        Jordan, Stephen
+        \textit{Quantum Algorithm Zoo}
+        math.nist.gov/quantum/zoo, Accessed 2017
+    \bibitem{}
+        Booth, Michael, Reinhardt, Steven P., Roy, Aidan
+        \textit{Partitioning Optimization Problems for Hybrid Classical/Quantum Execution}
+        D-Wave systems, 2017
+    \bibitem{}
+        Hen, Itay, Young, A. P.
+        \textit{Exponential Complexity of the Quantum Adiabatic Algorithm for certain Satisfiability Problems}
+        Department of Physics, UC Santa Cruz, 2011
+    \bibitem{}
+        Mandra, Salvatore, Guerreschi, Gian Giacomo, Aspuru-Guzik, Alan
+        \textit{Faster than Classical Algorithm for Dense Formulas of Exact Satisfiability and Occupation Problems}
+        Harvard University, 2016
+    \bibitem{}
+        Ambainis, Andris
+        \textit{Quantum Search Algorithms}
+        Archiv, Accessed 2017
+
 \end{thebibliography}

### 2017-05-16 scripts/run.py
Fixes indent in run script

@@ -85,7 +85,7 @@ def run(args):
     bname = basename(filename)
     if not os.path.exists(bname + '.v'):
         shutil.copy(filename, bname + '.v')
-        try:
+    try:
         a, b = to_output(bname, iterations)
         resulta = interpret_output(a)
         resultb = interpret_output(b)

### 2017-05-17 papers/paper.tex
Adds discussion rough draft (for sandia pres.)

@@
 This paper explores different interfaces in the hope of improving the availability of quantum problem solving, and demonstrating the ease of use of existing interfaces.
-\newpage
 
@@
 However, the effectiveness of this implementation is limited, and only useful for showing how the code scales with different solvers.
-\newpage
 
@@
 \lstinputlisting[label=samplecode,caption=Dynamic Programming]{../scripts/dynamic.py}
-\newpage
 
@@
 \lstinputlisting[label=samplecode,caption=Fully Polynomial Time Approximation Scheme]{../scripts/fptas.py}
-\newpage
 
@@
 \lstinputlisting[label=samplecode,caption=Greedy Knapsack Algorithm]{../scripts/greedy.py}
-\newpage
 
@@
 
-\newpage
 \begin{figure}[h!]
@@
 \end{enumerate}
-
-\newpage
 
@@
     ]{../csvs/single.csv}
-
-\newpage
 
@@
 
-\textit{SECTION IN PROGRESS}
+Quantum Computers currently do not help solve non trivial real world problems in an advantageous way.
+DWave currently has a superior interface, but has not proven an asymptotic advantage.
+The IBM interface is less usable for layprogrammers, but the gate model has been theoretically proven faster than the classical model of computation.
 
-Quantum Computers currently do not help solve non trivial real world problems in an advantageous way.
+In the future, IBM and Google plan on building 50-qubit gate model computers, which will hopefully be able to demonstrate experimental quantum speedups for the gate model.
+D-Wave also plans on extending its hardware, and will continue releasing more advanced Quantum Annealers.
+Hopefully, D-Wave can demonstrate an asymptotic advantage both theoretically and experimentally.
 
-DWave currently has a superior interface, but has not proven an asymptotic advantage.
+Because it has been theoretically proven, the Gate Model seems to likeliest to be successful in the future.
+However, it needs advanced methods for error correction, which need to be developed further for gate model quantum computation to become a reality.
+Also, it would be greatly improved with an additional layer of abstraction in the programming interface.
 
-The IBM Interface is less usable for layprogrammers, but the gate model has been theoretically proven faster than the classical model of computation.
+DWave needs to prove an asymptotic speedup, as well as developing its own fault-tolerance.
+Currently, there do not exist robust, realizable schemes for fault-tolerance in annealing systems.
+If these are developed, D-Wave also be a potential option for quantum computation in the future.
+
+Until these improvements happen, however, Quantum Computing will remain nothing more than an interesting topic for discussion.
 
@@
 
-\begin{thebibliography}{9}
-    \bibitem{}
+\begin{thebibliography}{11}
+    \bibitem{qknapsack}
+        Arvind, V., Schuler, Rainer
+        \textit{The Quantum Query Complexity of 0-1 Knapsack and Associated Claw Problems}
+        Archiv, Accessed 2017
+    \bibitem{qmapcolor}
+        Dahl, E. D.
+        \textit{Programming With the D-Wave: Map Coloring Problem}
+        D-Wave systems, 2013
+    \bibitem{qalgzoo}
+        Jordan, Stephen
+        \textit{Quantum Algorithm Zoo}
+        math.nist.gov/quantum/zoo, Accessed 2017
+    \bibitem{qopt}
+        Booth, Michael, Reinhardt, Steven P., Roy, Aidan
+        \textit{Partitioning Optimization Problems for Hybrid Classical/Quantum Execution}
+        D-Wave systems, 2017
+    \bibitem{qxsat0}
+        Hen, Itay, Young, A. P.
+        \textit{Exponential Complexity of the Quantum Adiabatic Algorithm for certain Satisfiability Problems}
+        Department of Physics, UC Santa Cruz, 2011
+    \bibitem{qxsat1}
+        Mandra, Salvatore, Guerreschi, Gian Giacomo, Aspuru-Guzik, Alan
+        \textit{Faster than Classical Algorithm for Dense Formulas of Exact Satisfiability and Occupation Problems}
+        Harvard University, 2016
+    \bibitem{qa-prolog0}
         Pakin, Scott
@@
         Cambridge University Press, 2017
-    \bibitem{}
+    \bibitem{qa-prolog1}
+        Ines Dutra
+        \textit{Constraint Logic Programming: a short tutorial}
+        University of Porto, 2010
+    \bibitem{grover0}
         Grover, Lok K.
@@
         Proceedings of 28th Symp Theory of Computing, 1996
-    \bibitem{}
+    \bibitem{grover1}
         John Wright
@@
         Carnegie Mellon University, 2015
-    \bibitem{}
-        Arvind, V., Schuler, Rainer
-        \textit{The Quantum Query Complexity of 0-1 Knapsack and Associated Claw Problems}
-        Archiv, Accessed 2017
-    \bibitem{}
-        Dahl, E. D.
-        \textit{Programming With the D-Wave: Map Coloring Problem}
-        D-Wave systems, 2013
-    \bibitem{}
-        Ines Dutra
-        \textit{Constraint Logic Programming: a short tutorial}
-        University of Porto, 2010
-    \bibitem{}
-        Jordan, Stephen
-        \textit{Quantum Algorithm Zoo}
-        math.nist.gov/quantum/zoo, Accessed 2017
-    \bibitem{}
-        Booth, Michael, Reinhardt, Steven P., Roy, Aidan
-        \textit{Partitioning Optimization Problems for Hybrid Classical/Quantum Execution}
-        D-Wave systems, 2017
-    \bibitem{}
-        Hen, Itay, Young, A. P.
-        \textit{Exponential Complexity of the Quantum Adiabatic Algorithm for certain Satisfiability Problems}
-        Department of Physics, UC Santa Cruz, 2011
-    \bibitem{}
-        Mandra, Salvatore, Guerreschi, Gian Giacomo, Aspuru-Guzik, Alan
-        \textit{Faster than Classical Algorithm for Dense Formulas of Exact Satisfiability and Occupation Problems}
-        Harvard University, 2016
-    \bibitem{}
+    \bibitem{grover2}
         Ambainis, Andris
@@
         Archiv, Accessed 2017
-
 \end{thebibliography}

### 2017-05-17 papers/essay.tex
Adds reflective essay

@@
 
-• What else have you learned about yourself? About your project topic?
-• Is the project topic something you are likely to pursue once senior projects are over?
-• Without a quiz, paper, test, homework assignment or teacher to motivate you, what has
-motivated you to work on your senior project this week? Is it purely getting through the
-last graduation requirement, or do you truly enjoy spending time on this project that you
-created? Is it hard to motivate yourself to spend time on the project? Write some ideas
-about what motivates you.
-• If your project were a class and you were the teacher, how would you assess/test/evaluate
-your students’ progress, understanding, skill? Would you give a written test based on
-knowledge, a hands-on demonstration of skill, or some other evaluation?
-• If you made a soundtrack to your senior project, what songs would you include and why?
-• Describe a metaphor for this experience. Fill in the blank and elaborate: This experience
-has been like...
-• What advice would you give next year’s seniors?
+During this project, I've read more than 30 publications: From Bell Labs, Sandia Labs, Los Alamos Labs, Harvard, Carnegie Mellon, MIT, IBM, NASA, and Microsoft.
+For every problem I've solved, I've probably found another dozen that are worth pursuing.
+Quantum Computing is a vast field, and I'm lucky to have been exposed to even a small percentage of it.
 
-% ==================================================
-\section{Appendix}
-% ==================================================
+As this project comes to a close, I feel that I've gained a layprogrammers perspective of running NP-Complete problems on different types of Quantum Computers.
+Since I'm unaffiliated with either IBM, Los Alamos, or DWave, I've been able to approach the problem from a neutral perspective, and recognize both the flaws and benefits of each implementation.
+In addition, I've grown close to the problem itself. I see instances of it in my daily life, and am continually impressed by how subtle it is.
+For instance, while I was completing my senior experience I was simultaneously hunting craigslist for used cars.
+I wanted to find a car with good mileage, high safety, enjoyable peripherals (like a stereo), and a low odometer reading, for the lowest price possible.
+
+Surprisingly, this is essentially an instance of the knapsack problem! 
+At home, at school, and in business, the Knapsack problem shows up.
+I appreciate the importance of solving this problem using Quantum Computation, and will be continuing my research with Los Alamos if possible, as well as working on similar problems at Sandia.
 

### 2017-05-17 scripts/dynamic.py
Reduces output in dynamic programming solution

@@ -55,9 +55,5 @@ def dynamic_knapsack(items, outerConstraints):
                     c - items[i - 1][n + 1] for n, c in enumerate(k)
                     ]
     result.reverse()
-
-    #print('Knapsack problem solved classically with {} static evaluations:'.format(len(bestvalue.cache)))
     choices = [items.index(choice) for choice in result]
     return bestvalue(len(items), outerConstraints), result, choices
-
-

### 2018-03-21 scripts/quant_exp.py
Removes figures from paper and adds optional imports

@@ -1,23 +1,32 @@
-from IBMQuantumExperience import IBMQuantumExperience
+try:
+    from IBMQuantumExperience import IBMQuantumExperience
 
-from pprint import pprint
+    from pprint import pprint
 
-def quant_exp(args):
-    with open('etc/IBMtoken', 'r') as infile:
-        token = infile.read().replace('\n', '')
-    config = {
-       "url": 'https://quantumexperience.ng.bluemix.net/api'
-    }
+    def quant_exp(args):
+        with open('etc/IBMtoken', 'r') as infile:
+            token = infile.read().replace('\n', '')
+        config = {
+           "url": 'https://quantumexperience.ng.bluemix.net/api'
+        }
 
-    QuantExp = IBMQuantumExperience.IBMQuantumExperience
-    api = QuantExp(token, config)
-    for code in api.get_last_codes():
-        pprint(code)
-        '''
-        name = code['name']
-        if 'grover' in name.lower():
-            print('IBM Results for{}'.format(name))
-            pprint(code['executions'][-1]['result'])
-            #pprint(code.keys())
-            #pprint(api.get_execution(name))
-        '''
+        QuantExp = IBMQuantumExperience.IBMQuantumExperience
+        api = QuantExp(token, config)
+        for code in api.get_last_codes():
+            pprint(code)
+            '''
+            name = code['name']
+            if 'grover' in name.lower():
+                print('IBM Results for{}'.format(name))
+                pprint(code['executions'][-1]['result'])
+                #pprint(code.keys())
+                #pprint(api.get_execution(name))
+            '''
+except ModuleNotFoundError:
+    print('IBM suite not installed')
+    #1/0
+
+    def quant_exp(args):
+        1/0
+
+

### 2018-03-21 scripts/run_qasm.py

@@ -1,24 +1,28 @@
-from QuantumComputer import *
+try:
+    from QuantumComputer import *
 
-def clean(line):
-    if '//' in line:
-        line, comment = line.split('//', 1)
-    return line
+    def clean(line):
+        if '//' in line:
+            line, comment = line.split('//', 1)
+        return line
 
-def run_qasm(args):
-    assert len(args) >= 1
-    filename = args[0]
-    if len(args) == 1:
-        containing = ['q0', 'q1', 'q2', 'q3', 'q4']
-    else:
-        containing = args[1:]
-    with open(filename, 'r') as qasmfile:
-        content = [clean(line) for line in qasmfile]
-    code = '\n'.join(content)
-    print(code)
-    qc = QuantumComputer()
-    qc.reset()
-    qc.execute(code)
-    for c in containing:
-        Probability.pretty_print_probabilities(qc.qubits.get_quantum_register_containing(c).get_state())
+    def run_qasm(args):
+        assert len(args) >= 1
+        filename = args[0]
+        if len(args) == 1:
+            containing = ['q0', 'q1', 'q2', 'q3', 'q4']
+        else:
+            containing = args[1:]
+        with open(filename, 'r') as qasmfile:
+            content = [clean(line) for line in qasmfile]
+        code = '\n'.join(content)
+        print(code)
+        qc = QuantumComputer()
+        qc.reset()
+        qc.execute(code)
+        for c in containing:
+            Probability.pretty_print_probabilities(qc.qubits.get_quantum_register_containing(c).get_state())
 
+except ModuleNotFoundError:
+    print('QuantumComputer module not installed')
+    #1/0
